### 2017-11-20 Risk analysis/Text/Layout/Layout/chapter1.tex
Enough for today

Bayesian methods are an intuitive approach to inference, naturally inherent in human thinking patterns and closely tied to processes of decision-making \citep{berger2013stat, davidson2015, jaynes1986bayesian}. Individuals are constantly faced with situations in which a decision has to be made, but only incomplete information is available. Such a problem necessitates an approach based on plausible reasoning, one which is intuitively structured in five stages \citep{jaynes1986bayesian}:

@@

This work builds upon their concept, exploring the potential significance their findings might have in the context of decision-making. Bayesian decision-theory is to be included in the step of model evaluation. This is achieved by assigning an economic meaning to the structural model and designing a case-specific custom loss functions to find decisions which are optimal related to the state of knowledge and the preferences of actor's with different risk-affinities. More specifically, the models are designed to represent potential petroleum systems. Consequently, the development of algorithms for automatic hydrocarbon trap recognition and volume calculation represent a central part of this work.\\

>>>>

Bayesian methods are an intuitive approach to inference, naturally inherent in human thinking patterns and closely tied to processes of decision-making \citep{berger2013stat, davidson2015, jaynes1986bayesian}. Individuals are constantly faced with situations in which a decision has to be made, but only incomplete information is available. Such a problem necessitates an approach based on plausible reasoning, one which is intuitively structured in four stages \citep{jaynes1986bayesian}:

@@

This work builds upon their concept, exploring the potential significance their findings might have in the context of decision-making. Bayesian decision-theory is to be included in the step of model evaluation. This is achieved by assigning an economic meaning to the structural model and designing a case-specific custom loss functions to find decisions which are optimal related to the state of knowledge and the preferences of actors with different risk-affinities. More specifically, the models are designed to represent potential petroleum systems. Consequently, the development of algorithms for automatic hydrocarbon trap recognition and volume calculation represent a central part of this work.\\

### 2017-11-20 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Enough for today

        \subsection{Bayesian inference}
        Bayesian inference is most importantly characterized by its preservation of uncertainty, in contrast to standard statistical inference \citep{davidson2015}. Probability is seen as a measure of belief for an event to occur. It has been argued by \cite{davidson2015}  that this Bayesian approach is intuitive and inherent in the natural human perspective. These beliefs can be assigned to individuals. Thus, different and even contradicting beliefs about the probability of an event might be held by different individuals, based on variations and disparities in the information available to each one individual \citep{davidson2015}.\\
        The initial belief or guess about an event $\theta$ can be denoted as $p(\theta)$ \citep{davidson2015, delaVarga2016}. This is used as the so-called prior probability on which Bayesian updating is based. The beliefs about the occurrence of an event are revalued in the presence of additional information, i.e. the observation of new evidence $y$. These observations are included as likelihoods $p(y|\theta)$. This process of updating results in a posterior probability $p(\theta|y)$ \citep{davidson2015, delaVarga2016}. It is important to note that the prior is not simply discarded but re-weighted by Bayesian updating. It was also pointed out by \citet{davidson2015} that by utilizing an uncertain prior, the potential for wrongfulness of the initial guess is already included. This means that Bayesian updating is about reducing uncertainty in a belief and reaching a guess that is less wrong \citep{davidson2015}.
        Bayesian inference is defined by and conducted via the following equation, called the Bayes' Theorem \citep{davidson2015}:
        \begin{equation}\label{eq:BayesTheorem}
        p(\theta|y) = \frac{p(y|\theta)p(\theta)}{p(y)}
        \propto p(y|\theta)p(\theta).
        \end{equation}

@@

        The magnitude of an estimate's loss is defined by a loss function, which is a function of the estimate of the parameter and the true value of the parameter \citep{davidson2015}:        

@@

        The presence of uncertainty during decision making implies that the true parameter is unknown and thus the truly incurred loss $L(\theta,a)$ cannot be known at the time of making the decision \citep{berger2013stat, davidson2015}. The Bayesian perspective considers unknown parameters as random variables and samples that are drawn from the posterior distribution as possible realizations of the unknown parameter, i.e. all possible true values are represented by this distribution \citep{davidson2015}. A suitable alternative to the actual loss is to consider each decision's expected loss and to make a decision that is optimal in relation to this expected loss \citep{berger2013stat}. \\        

@@

        The expectation symbol $E$ is subscripted with $\theta$, by which it is indicated that $\theta$ is the respective unknown variable. This expected loss is also referred to as the risk of estimate $\hat{\theta}$ \citep{davidson2015}.\\        
        By the Law of Large Numbers, the expected loss of $\hat{\theta}$ can be approximated drawing a large sample size $N$ from the posterior distribution, respectively applying a loss function $L$ and averaging over the number of samples \citep{davidson2015}:

@@

        \section{Application in structural geological modeling}\label{sec:bayes_in_struc_modeling}
        In this work, these methods of Bayesian analysis and decision theory are applied in the field of geological structural modeling. The fundamental approach follows closely the research conducted by \citet{delaVarga2016} and builds upon their findings.\\
        According to them, structural geological modeling can be regarded as a forward problem and the elements of Bayesian inference can be specified in this context as follows:
        \begin{enumerate}
        	\item \textbf{Mathematical forward model ($M$)}: The connections between parameters $\theta$ and observed data $y$ are defined in such mathematical models. According to \citet{delaVarga2016}, the realization of a geological model $M$ can be regarded as a direct function of a set of input parameters:
        	\begin{equation}
        	M = f(\vec{x}, \phi_i, k_j, \alpha_k, \beta_l)\label{eq:forward_model},
        	\end{equation}
        	where $\phi_i$ is a function of position $\vec{x}$, more precisely an interpolation function, to which respective additional parameters are given by $\alpha_k$. Available primary geological information, such as positions and dips of layer interfaces and in the subsurface, is represented by $k_j$. A topological description, such as the relationships between faults and layer surfaces, is given by $\beta_l$. An essential aspect of this function is that it allows for a full automation of the modeling step, so that the consequences of a change in an input parameter are realized directly without the need for any further manual inspection or interaction \citep{wellmann2017sandstone, delaVarga2016}. The modeling step and the respective interpolation method used in this work are presented in Section \ref{sec:struc_geo_modeling} below.
        	\item \textbf{Model parameters ($\theta$)}: These model-defining parameters can be deterministic or stochastic. In the latter case, they are uncertain parameters to which a probability distribution is assigned. Regarding Equation \ref{eq:forward_model} above, these can be any of the factors $\vec{x}$, $k_j$, $\alpha_k$ and $\beta_l$, which define the realization of the forward model over $\phi_i$.
        	\item \textbf{Observed data ($y$)}: This is any type of additional information that can be related to the forward modeling results and might possibly be used to reduce uncertainty. Such data can be gained by measurements and observations, for example by core sampling, well-log analysis or seismic acquisition. 
        	\item \textbf{Likelihood functions $p(y|\theta)$}: Links between the previous parameters $\theta$ and the additional data $y$ are established by these functions in way that they reflect the likelihood of the parameter states given the observations. They mathematically defined in the same way as probability functions, but are a function of the data $y$, instead of the parameters $\theta$ \citep{delaVarga2016}.
        \end{enumerate}

@@

        \subsection{Visualizing uncertainty}
        \begin{figure}
	        \centering
	        \includegraphics[width=1\textwidth]{Figures/information_entropy.png}
	        \caption{Illustrations depicting the concept of information entropy to visualize uncertainties in spatial applications. In (a), a map composed of uncertain units is subdivided into a regular grid of equally sized cells. The probabilities of possible outcomes regarding each unit is estimated for each cell in (b). From this results a map of cell information entropies (c), with the highest values where all units can occur equally frequent, and lowest for cells where no uncertainty is given and entropy is zero (from \citet{wellmann2012uncertainties}).}\label{fig:information_entropy}
        \end{figure}
        Information entropy was first defined by \citet{shannon1948mathematical} and adopted as a method to visualize uncertainties in 3D geological models by \citet{wellmann2012uncertainties}. This approach was later also used by \citet{delaVarga2016} and \citet{schaaf2017}. Information entropy is applied to predict the model accuracy at every location in the model space by visualizing its respective uncertainty and thus returning a measure for the quality of the model. This is achieved by subdiving the model space into a regular raster of equally sized cells (voxels) and measuring the accuracy for every such cell. In the context of geological modeling, the central question is based on the knowledge of how frequent a single geological feature occurs in a voxel \citep{wellmann2012uncertainties}. \citet{de1972definition} established that information entropy can serve as a measure of fuzziness, a concept described by \citet{zadeh1965fuzzy}. Given a fuzzy set in which fuzziness of each part is indicated by $f\in [0,1]$, the following conditions hold:
        \begin{enumerate}
	        \item The measure should only be 0 if $f$ is 0 or 1 in every cell.
	        \item The measure is maximal given $f = 0.5$ in every cell \citep{wellmann2012uncertainties}.
        \end{enumerate}
        While the first condition represents the complete absence of uncertainty everywhere in the model, the second condition is met in the opposite case of full uncertainty in the whole model space, i.e. all outcomes are equally likely in each cell \citep{schaaf2017}. From this, \citet{wellmann2012uncertainties} derived the following equation for application in geological modeling:
        \begin{equation}
	        H_m = -\frac{1}{N}*\sum_{x=1}^{N}[p_m(x)*\log(p_m(x))+(1-p_m(x))*\log(1-p_m(x))],
        \end{equation}
        in which $f$ is denoted as the probability $p_m$ of an outcome $m\in M$ in a cell with a position $x$. The fuzziness is quantified as the entropy $H_m$, normalized by the total number of cells $N$. Subsequently, a total information entropy can be calculated for a model as \citep{wellmann2012uncertainties}:
        \begin{equation}
	        H_T = -\frac{1}{N}\sum_{x=1}^{N}H(x).
        \end{equation}
        This total entropy $H_T$ is 0 when no uncertainty is found in any cell, oppositely it is maximal in the case of equal likelihood of outcoms in every cell \citep{wellmann2012uncertainties, schaaf2017}. The application of these entropy measures allows for the calculation and visualization of uncertainties in each voxel, the assessment of uncertainties of entire geological units, as well as the quantification of total model uncertainty represented by a single number \citep{wellmann2012uncertainties}.

@@

		\begin{equation}\label{eq:LF_final}
		L(\theta,\hat{\theta}) =
		\begin{cases}
		|\theta - \hat{\theta}|, & \text{for } 0<\hat{\theta}<\theta  \\
		|\theta-\hat{\theta}|*a, & \text{for } 0<\theta<\hat{\theta} \\
		|\theta-\hat{\theta}|*b, & \text{for } \theta\leq0<\hat{\theta} \\
		|\theta-\hat{\theta}|*c, & \text{for } \hat{\theta}\leq0<\theta 
		\end{cases},
		\text{ with } a,b,c \in \mathbb{Q}.
		\end{equation}  
		It is important to note that the weighting factors defined above can take basically any numerical values but should be chosen in a way that they appropriately represent the framework conditions of the problem. Here, based on the considerations named above, it is assumed that normal overestimation is 25\% (\textit{a} = 1.25), fatal overestimation 100\% (\textit{b} = 2) and fatal underestimation 50\% (\textit{c} = 1.5) worse than normal underestimation. \\		
		It has to be emphasized that this is just one possible proposal for loss function customization. There exists not one perfect design for such a case. Slight to strong changes can already be implemented by simply varying the values of the weighting factors \textit{a, b} and \textit{c}. Fundamentally different loss functions can also be based on a significantly different mathematical structure. Loss functions are customized regarding the problem environment and according to the to subjective needs and objectives of decision-maker. Thus, they are mostly defined by the actor expressing his perspective. Changes in the individual's perception and attitude might lead to further customization needs at a future point in time. Especially considering individual persons as actors, psychological aspects may play a significant role.

@@

			\includegraphics[width=1\textwidth]{Figures/1D_principle.PNG}
			\caption{Conceptual illustration of applying Bayesian inference in an abstract 1D geological model as conducted by \citet{delaVarga2016}. Prior distributions of layer boundaries in depth (a) are updated using thickness likelihoods (b) to attain posterior distributions (c). Model parameters which are uncorrelated in their joint probability distribution before the inference (d), are correlated after performing Bayesian inference (e) (from \citet{delaVarga2016}).}\label{fig:1D_principle}
			\subsection{Bayesian inference and analysis of the 1D case}\label{sec:1D_bayes}
			For conducting Bayesian inference, it is assumed that new observations are made, providing additional information on the likelihoods of the thicknesses of the two layers of interest. Likelihood functions for reservoir and seal thicknesses are introduced based on another set of normal probability distributions. These are directly related to the layer boundary positions, i.e. the prior parameter distributions. Means and standard deviations of the likelihood distributions are variable, so that several scenarios based on the assumption of different observations can be tested. Parameter priors and likelihood functions are embedded into a probabilistic modeling framework as described in Section \ref{sec:numerical_implementation} and MCMC sampling is conducted accordingly. Performing Bayesian inference on such a 1D geological model follows the conceptual example devised by \citet{delaVarga2016} (see Figure \ref{fig:1D_principle}). Posterior distributions are to be evaluated based on the valuation method described in the following.

@@

		\subsection{Design of the 3D geological reservoir model}\label{sec:3D_design}
		For the purpose of exploring the application and effects of Bayesian analysis and decision theory in this work, the model is nevertheless to be kept conceptual and relatively simple. Stratigraphically, it is designed to include one main reservoir unit (sandstone), one main seal unit (shale), an underlying basement through which hydrocarbon fluids could have flown upwards and overlying formations that are assumed to be permeable, so that hydrocarbons can escape upwards. Structurally, it is constructed to feature an anticlinal fold that is displaced by a normal fault. All layers are tilted so that they dip in the opposite direction of the fault plane dip. The original concept of this model is designed in a way, that a potential hydrocarbon trap is formed in the reservoir rock enclosed by the deformed seal and the normal fault.\\
		This trap, more specifically the trap volume, is defined as the central feature of economic interest. For conducting simple and straightforward volumetric calculations, it is assumed that found closed traps are always filled to spill with oil, i.e. the complete trap volume is hydrocarbon filled and the $OOIP$ can be attained over this volume.\\
		The maximum trap volume is assumed to equate the hydrocarbon-filled rock volume $A * h$ in Equation \ref{eq:OOIP} and is thus to be used to valuate each realization of the geological model. Single results are expected to vary, depending on the uncertain input parameters defined in Section \ref{sec:3D_construction} below. The custom loss function \ref{eq:LFR_final} is to be applied on the resulting value distributions before and after performing Bayesian inference. This way, the effect of incorporating additional information in the form of likelihoods is to be assessed from a perspective of Bayesian decision theory. It is furthermore assumed that the hydrocarbon trap volume is directly linked to a project development decision, i.e. investment and allocation of resources is represented by bidding on a volume estimate.

>>>>

        \subsection{Bayesian inference}
        Bayesian inference is most importantly characterized by its preservation of uncertainty, in contrast to standard statistical inference \citep{box2011bayesian, jaynes2003probability, harney2013bayesian, davidson2015}. The Bayesian approach is widely seen as intuitive and inherent in the natural human perspective. Probability is seen as a measure of belief for an event to occur. These beliefs can be assigned to individuals. Thus, different and even contradicting beliefs about the probability of an event might be held by different individuals, based on variations and disparities in the information available to each one individual.\\
        The initial belief or guess about an event $\theta$ can be denoted as $p(\theta)$. This is used as the so-called prior probability on which Bayesian updating is based. The beliefs about the occurrence of an event are revalued in the presence of additional information, i.e. the observation of new evidence $y$. These observations are included as likelihoods $p(y|\theta)$. By conducting this process of inference, a posterior probability $p(\theta|y)$ is attained. It is important to note that the prior is not simply discarded but re-weighted by Bayesian inference. By utilizing an uncertain prior, the potential for wrongfulness of the initial guess is already included. This means that Bayesian updating is about reducing uncertainty in a belief and reaching a guess that is less wrong. Bayesian inference is defined by and conducted via the following equation, called the Bayes' Theorem \citep{box2011bayesian, jaynes2003probability, harney2013bayesian, davidson2015}:
        \begin{equation}\label{eq:BayesTheorem}
        p(\theta|y) = \frac{p(y|\theta)p(\theta)}{p(y)}
        \propto p(y|\theta)p(\theta).
        \end{equation}

@@

        The magnitude of incurred loss related to an estimate is defined by a loss function, which is a function of the estimate of the parameter and the true value of the parameter \citep{wald1950statistical, davidson2015}:        

@@

        The presence of uncertainty during decision making implies that the true parameter is unknown and thus the truly incurred loss $L(\theta,a)$ cannot be known at the time of making the decision \citep{berger2013stat, davidson2015}. The Bayesian perspective considers unknown parameters as random variables and samples that are drawn from the posterior distribution as possible realizations of the unknown parameter, i.e. all possible true values are represented by this distribution \citep{davidson2015}. A probabilistic alternative to the actual loss is to consider each decision's expected loss and to make a decision that is optimal in relation to this expected loss \citep{berger2013stat}. \\        

@@

        The expectation symbol $E$ is subscripted with $\theta$, by which it is indicated that $\theta$ is the respective unknown variable. This expected loss $l$ is also referred to as the risk of estimate $\hat{\theta}$ \citep{davidson2015}.\\        
        By the Law of Large Numbers, the expected loss of $\hat{\theta}$ can be approximated drawing a large sample size $N$ from the posterior distribution, respectively applying a loss function $L$ and averaging over the number of samples \citep{davidson2015}:

@@

        \section{Application in structural geological modeling}\label{sec:bayes_in_struc_modeling}
        In this work, these methods of Bayesian analysis and decision theory are applied in the field of geological structural modeling. The fundamental approach follows closely the research conducted by \citet{delaVarga2016} and builds upon their findings.\\
        According to them, structural geological modeling can be regarded as a forward problem and the elements of Bayesian inference can be specified in this context as follows:
        \begin{enumerate}
        	\item \textbf{Mathematical forward model ($M$)}: The connections between parameters $\theta$ and observed data $y$ are defined in such mathematical models. According to \citet{delaVarga2016}, the realization of a geological model $M$ can be regarded as a direct function of a set of input parameters:
        	\begin{equation}
        	M = f(\vec{x}, \phi_i, k_j, \alpha_k, \beta_l)\label{eq:forward_model},
        	\end{equation}
        	where $\phi_i$ is a function of position $\vec{x}$, more precisely an interpolation function, to which respective additional parameters are given by $\alpha_k$. Available primary geological information, such as positions and dips of layer interfaces, is represented by $k_j$. A topological description, such as the relationships between faults and layer surfaces, is given by $\beta_l$. An essential aspect of this function is that it allows for a full automation of the modeling step, so that the consequences of a change in an input parameter are realized directly without the need for any further manual inspection or interaction \citep{wellmann2017sandstone, delaVarga2016}. The modeling step and the respective interpolation method used in this work are presented in Section \ref{sec:struc_geo_modeling} below.
        	\item \textbf{Model parameters ($\theta$)}: These model-defining parameters can be deterministic or stochastic. In the latter case, they are uncertain parameters to which a probability distribution is assigned. Regarding Equation \ref{eq:forward_model} above, these can be any of the factors $\vec{x}$, $k_j$, $\alpha_k$ and $\beta_l$, which define the realization of the forward model over $\phi_i$.
        	\item \textbf{Observed data ($y$)}: This is any type of additional information that can be related to the forward modeling results and might possibly be used to reduce uncertainty. Such data can be gained by measurements and observations, for example by core sampling, well-log analysis or seismic acquisition. 
        	\item \textbf{Likelihood functions $p(y|\theta)$}: Links between the previous parameters $\theta$ and the additional data $y$ are established by these functions in way that they reflect the likelihood of the parameter states given the observations. They mathematically defined in the same way as probability functions, but are a function of the data $y$, instead of the parameters $\theta$ \citep{delaVarga2016}.
        \end{enumerate}

@@

        \subsection{Visualizing uncertainty}
        \begin{figure}
	        \centering
	        \includegraphics[width=1\textwidth]{Figures/information_entropy.png}
	        \caption{Illustrations depicting the concept of information entropy to visualize uncertainties in spatial applications. In (a), a map composed of uncertain units is subdivided into a regular grid of equally sized cells. The probabilities of possible outcomes regarding each unit is estimated for each cell in (b). From this results a map of cell information entropies (c), with the highest values where all units can occur equally frequent, and lowest for cells where no uncertainty is given and entropy is zero (from \citet{wellmann2012uncertainties}).}\label{fig:information_entropy}
        \end{figure}
        Information entropy was first defined by \citet{shannon1948mathematical} and adopted as a method to visualize uncertainties in 3D geological models by \citet{wellmann2012uncertainties}. This approach was later also used by \citet{delaVarga2016} and \citet{schaaf2017}. Information entropy is applied to predict the model accuracy at every location in the model space by visualizing its respective uncertainty and thus returning a measure for the quality of the model. This is achieved by subdiving the model space into a regular raster of equally sized cells (voxels) and measuring the accuracy for every such cell. In the context of geological modeling, the central question is based on the knowledge of how frequent a single geological feature occurs in a voxel \citep{wellmann2012uncertainties}. \citet{de1972definition} established that information entropy can serve as a measure of fuzziness, a concept described by \citet{zadeh1965fuzzy}. Given a fuzzy set in which fuzziness of each part is indicated by $f\in [0,1]$, the following conditions hold:
        \begin{enumerate}
	        \item The measure should only be 0 if $f$ is 0 or 1 in every cell.
	        \item The measure is maximal given $f = 0.5$ in every cell \citep{wellmann2012uncertainties}.
        \end{enumerate}
        While the first condition represents the complete absence of uncertainty everywhere in the model, the second condition is met in the opposite case of full uncertainty in the whole model space, i.e. all outcomes are equally likely in each cell \citep{schaaf2017}. From this, \citet{wellmann2012uncertainties} derived the following equation for application in geological modeling:
        \begin{equation}
	        H_m = -\frac{1}{N}*\sum_{x=1}^{N}[p_m(x)*\log(p_m(x))+(1-p_m(x))*\log(1-p_m(x))],
        \end{equation}
        in which $f$ is denoted as the probability $p_m$ of an outcome $m\in M$ in a cell with a position $x$. The fuzziness is quantified as the entropy $H_m$, normalized by the total number of cells $N$. Subsequently, a total information entropy can be calculated for a model as \citep{wellmann2012uncertainties}:
        \begin{equation}
	        H_T = -\frac{1}{N}\sum_{x=1}^{N}H(x).
        \end{equation}
        This total entropy $H_T$ is 0 when no uncertainty is found in any cell, oppositely it is maximal in the case of equal likelihood of outcomes in every cell \citep{wellmann2012uncertainties, schaaf2017}. The application of these entropy measures allows for the calculation and visualization of uncertainties in each voxel, the assessment of uncertainties of entire geological units, as well as the quantification of total model uncertainty represented by a single number \citep{wellmann2012uncertainties}.

@@

		\begin{equation}\label{eq:LF_final}
		L(\theta,\hat{\theta}) =
		\begin{cases}
		|\theta - \hat{\theta}|, & \text{for } 0<\hat{\theta}<\theta  \\
		|\theta-\hat{\theta}|*a, & \text{for } 0<\theta<\hat{\theta} \\
		|\theta-\hat{\theta}|*b, & \text{for } \theta\leq0<\hat{\theta} \\
		|\theta-\hat{\theta}|*c, & \text{for } \hat{\theta}\leq0<\theta 
		\end{cases},
		\text{ with } a,b,c \in \mathbb{Q}.
		\end{equation}  
		It is important to note that the weighting factors defined above can take basically any numerical values but should be chosen in a way that they appropriately represent the framework conditions of the problem. Here, based on the considerations named above, it is assumed that normal overestimation is 25\% (\textit{a} = 1.25), fatal overestimation 100\% (\textit{b} = 2) and fatal underestimation 50\% (\textit{c} = 1.5) worse than normal underestimation. \\		
		It has to be emphasized that this is just one possible proposal for loss function customization. There exists not one perfect design for such a case. Slight to strong changes can already be implemented by simply varying the values of the weighting factors \textit{a, b} and \textit{c}. Fundamentally different loss functions can also be based on a significantly different mathematical structure. Loss functions are customized regarding the problem environment and according to the subjective needs and objectives of the decision-maker. Thus, they are mostly defined by the actor expressing his perspective. Changes in the individual's perception and attitude might lead to further customization needs at a future point in time, as was reported by \citet{hennig2007}. Especially considering individual persons as actors, psychological aspects may play a significant role.

@@

			%\includegraphics[width=1\textwidth]{Figures/1D_principle.PNG}
			%\caption{Conceptual illustration of applying Bayesian inference in an abstract 1D geological model as conducted by \citet{delaVarga2016}. Prior distributions of layer boundaries in depth (a) are updated using thickness likelihoods (b) to attain posterior distributions (c). Model parameters which are uncorrelated in their joint probability distribution before the inference (d), are correlated after performing Bayesian inference (e) (from \citet{delaVarga2016}).}\label{fig:1D_principle}
			%\subsection{Bayesian inference and analysis of the 1D case}\label{sec:1D_bayes}
			For conducting Bayesian inference, it is assumed that new observations are made, providing additional information considered here in the form of likelihood functions for the thicknesses of the two layers of interest. Likelihood functions for reservoir and seal thicknesses are introduced based on another set of normal probability distributions. These are directly related to the layer boundary positions, i.e.\ the prior parameter distributions. Means and standard deviations of the likelihood distributions are variable, so that several scenarios based on the assumption of different observations can be tested. Parameter priors and likelihood functions are embedded into a probabilistic modeling framework as described in Section \ref{sec:numerical_implementation} and MCMC sampling is conducted accordingly. Performing Bayesian inference on such a 1D geological model follows the conceptual example devised by \citet{delaVarga2016}. Posterior distributions are to be evaluated based on the valuation method described in the following.

@@

		\subsection{Design of the 3D geological reservoir model}\label{sec:3D_design}
		For the purpose of exploring the application and effects of Bayesian analysis and decision theory in this work, the model is nevertheless to be kept conceptual and relatively simple. Stratigraphically, it is designed to include one main reservoir unit (sandstone), one main seal unit (shale), an underlying basement through which hydrocarbon fluids could have flown upwards and overlying formations that are assumed to be permeable, so that hydrocarbons can escape upwards. Structurally, it is constructed to feature an anticlinal fold that is displaced by a normal fault. All layers are tilted so that they dip in the opposite direction of the fault plane dip. The original concept of this model is designed in a way that a potential hydrocarbon trap is formed in the reservoir rock enclosed by the deformed seal and the normal fault.\\
		This trap, more specifically the trap volume, is defined as the central feature of economic interest. For conducting simple and straightforward volumetric calculations, it is assumed that found closed traps are always filled to spill with oil, i.e. the complete trap volume is hydrocarbon filled and the $OOIP$ can be attained over this volume.\\
		The maximum trap volume is assumed to equate the hydrocarbon-filled rock volume $A * h$ in Equation \ref{eq:OOIP} and is thus to be used to valuate each realization of the geological model. Single results are expected to vary, depending on the uncertain input parameters defined in Section \ref{sec:3D_construction} below. The custom loss function \ref{eq:LFR_final} is to be applied on the resulting value distributions before and after performing Bayesian inference. This way, the effect of incorporating additional information in the form of likelihoods is to be assessed from a perspective of Bayesian decision theory. It is furthermore assumed that the hydrocarbon trap volume is directly linked to a project development decision, i.e. investment and allocation of resources is represented by bidding on a volume estimate.
